\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\geometry{margin=1in}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdfpagemode=FullScreen,
}

% Section formatting
\titleformat{\section}{\bfseries\Large\color{black}}{}{0em}{}
\titleformat{\subsection}{\bfseries\normalsize\color{black}}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Dr. Charley Garcia}}\\[0.5em]
    \href{mailto:drcharley@protonmail.com}{drcharley@protonmail.com} \,|\,
    \href{https://www.linkedin.com/in/charliegarcia77/}{LinkedIn} \,|\,
    \href{https://codepen.io/RPhil86/full/ZYGMOmx}{Portfolio}
\end{center}

\section*{Professional Summary}
Retired technology leader with over 20 years of experience in software development, systems architecture, and robotics engineering. Team-oriented and innovative thinker, adept at assessing complex challenges and delivering scalable, high-impact solutions. Proven expertise in leading high-performance teams, mentoring talent, and driving operational excellence in global technology environments.

\section*{Skills and Certifications}
\subsection*{Skills}
\begin{itemize}[leftmargin=1.5em]
    \item Solution Architecture
    \item Telecommunications
    \item Service-Oriented Architecture (SOA)
    \item Networking and Infrastructure Management
    \item Software Development: HTML, CSS, JavaScript, Adobe Suite
    \item Leadership: Team mentoring, project management, strategic planning
\end{itemize}

\subsection*{Certifications}
\begin{itemize}[leftmargin=1.5em]
    \item Java Certificate
    \item MCSE: Private Cloud
    \item VMware VCP6 - Cloud
    \item Microsoft Certified Solutions Associate
    \item JavaScript Certification
\end{itemize}

\section*{Professional Experience}
\subsection*{Director of Software Development \hfill Oracle Corporation, NYC \newline January 2016 -- March 2019}
\begin{itemize}[leftmargin=1.5em]
    \item Led multiple engineering teams to develop and maintain critical services, workflow engines, and customer-facing applications.
    \item Delivered scalable technology solutions improving efficiency and performance.
    \item Mentored talent, recruited top-tier engineers, and raised standards.
    \item Ensured robust, global-scale software system deployments.
\end{itemize}

\subsection*{Creative Software Design Director \hfill Oracle Corporation, NYC \newline September 2010 -- March 2016}
\begin{itemize}[leftmargin=1.5em]
    \item Led software initiatives aligned with evolving business needs.
    \item Promoted engineering excellence and streamlined development.
    \item Designed scalable systems with cross-functional collaboration.
\end{itemize}

\subsection*{Senior IT Manager \hfill KED Technology Solutions, NYC \newline January 2001 -- December 2015}
\begin{itemize}[leftmargin=1.5em]
    \item Oversaw major infrastructure and telephony upgrades.
    \item Managed IT purchasing and license compliance.
    \item Led help desk operations ensuring enterprise-wide continuity.
\end{itemize}

\subsection*{Computer Technology Coach \hfill Newark Board of Education, NJ \newline January 2004 -- December 2014}
\begin{itemize}[leftmargin=1.5em]
    \item Taught students tech literacy, coding, and responsible usage.
    \item Created engaging, age-appropriate learning modules.
\end{itemize}

\subsection*{Senior CIO / Consultant \hfill Oracle Corporation, NYC \newline March 2001 -- December 2011}
\begin{itemize}[leftmargin=1.5em]
    \item Delivered strategic planning and rapid implementation.
    \item Streamlined development with efficient methodologies.
\end{itemize}

\subsection*{Creative Director \hfill NBCUniversal, NYC \newline December 2007 -- December 2010}
\begin{itemize}[leftmargin=1.5em]
    \item Built creative licensing strategies for global branding.
    \item Produced assets across multiple media categories.
    \item Supported international teams with marketing materials.
\end{itemize}

\subsection*{Developer \hfill Sun Technologies, NYC \newline March 2004 -- March 2006}
\begin{itemize}[leftmargin=1.5em]
    \item Designed courseware using Adobe and HTML/CSS.
    \item Updated training tools for telecom technical teams.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Research Doctorate, Advanced Software Systems} \\ Stanford University, August 2015 -- May 2018
    \item \textbf{PhD in Genetics and Genomics} \\ Boston University, August 2016 -- May 2017
    \item \textbf{Doctorate of Computer Science} \\ Georgia Tech, January 2015 -- December 2015
    \item \textbf{Doctorate in Robotics and Engineering} \\ DePaul University, August 2010 -- May 2013
    \item \textbf{Master of Arts, Software Engineering} \\ NYIT, August 2005 -- May 2009
\end{itemize}

\subsection*{Academic Note}
Doctoral degrees were earned through rigorous online programs at prestigious institutions, involving advanced coursework, independent research, and dissertations.

\end{document}
